We did an amazing thing

### 2023-01-10 paper.tex
Add another example (ellipses)

\section{Problem of verification}
\label{sec:verify}
In paper\textcolor{red}{our paper} we tested these algorithms against known
analytic solutions. Although we obtained acceptable results in the cases of
overlapping balls and disks, we were not sure if our algorithm performs good in
general and searched for more test cases. Here we present one such case:
two-dimensional sets with smooth boundary.

\subsection{Surface-surface function in two-dimensional case}
\label{sec:fss-2d}
\begin{figure}
  \centering
  \includegraphics[width=\linewidth]{images/Fss.png}
  \caption[]{Illustration of how $F_{ss}(\bm{r})$ is calculated. The interface
    between solid and void phases is a solid black curve. This interface
    translated by the vector $\bm{r}$ is show as a red solid curve. Support of
    $f_\Gamma(\bm{x}; \Delta)$ is a dashed ring. Shaded regions contribute to
    the surface-surface function.}
  \label{fig:Fss-explained}
\end{figure}
Let $S$ be some set in $\mathbb{R}^2$ which has a smooth boundary $\Gamma$ in
the sense that the boundary has a tangent line at every point. Now we introduce
a function $f_\Gamma(\bm{x}; \Delta)$:
\begin{equation*}
  f_\Gamma(\bm{x}; \Delta) = \left\{
  \begin{array}{ll}
    1/\epsilon & \quad \rho(\bm{x}, \Gamma) < \Delta \\
    0 & \quad \text{otherwise}
  \end{array}
  \right.
\end{equation*}
Here $\rho(\bm{x}, \Gamma)$ means a closest distance from point $\bm{x}$ to the
boundary $\Gamma$.

\begin{figure}
  \centering
  \includegraphics[width=\linewidth]{images/fss-zoomed.png}
  \caption[]{Zoomed image of intersection between the interface $\Gamma$ and its
    translated version $\Gamma'$. $\phi$ is an angle between tangent lines to
    the interfaces. Surface of dashed area is $\frac{\Delta^2}{\sin \phi}$.}
  \label{fig:fss-zoomed}
\end{figure}
Now define a functional sequence $F_{ss}(\bm{x}; \Delta)$:
\begin{align*}
  F_{ss}(\bm{r}; \Delta) &= \int\int f_\Gamma(\bm{x}; \Delta) f_\Gamma(\bm{x}
  + \bm{r}; \Delta) dx dy \\
  &= \sum_{k=1}^N S_k/\Delta^2
\end{align*}
Here $N$ is a number of intersections of $\Gamma$ with itself translated by a
vector $\bm{r}$ and $S_k$ is a surface of each such intersection (see
\cref{fig:Fss-explained}).
When $\Delta$ tends to zero, the boundary at the point of intersection can
be replaced with a tangent line at the point of intersection
(\cref{fig:fss-zoomed}). We get an expression for a surface of
intersection: $S_k = \frac{\Delta^2}{\sin \phi_k}$ where $\phi_k$ is an
acute angle between tangent lines. Hence, we get the following equation:
\begin{equation}
  F_{ss}(\bm{r}) = \lim_{\Delta \to 0} F_{ss}(\bm{r}; \Delta) =
  \sum_{k=1}^N \frac{1}{\sin \phi_k} \label{eq:fss-2d}
\end{equation}
It's easy to show that
$\lim_{\Delta \to 0} f_\Gamma(\bm{x}; \Delta) = |\nabla \chi_S(\bm{x})|$
and therefore \cref{eq:fss-2d} and \cref{eq:fss} define the same function.

@@

\section{Examples of two-dimensional sets with smooth boundary}
\label{seq:examples}
\subsection{A square}
Let's define a function $f(x, y) = \max(|x|, |y|)$. A set $f(x, y) \le T$ is a
square with side $2T$. The function $f$ is differentiable at all points where
$f(x, y) = T$ with exception of points $(-T, -T)$, $(-T, T)$, $(T, -T)$ and
$(T, T)$. The surface-surface correlation function for a square is equal to:
\begin{equation*}
  F_{ss}(x, y) = \left\{
  \begin{array}{ll}
    2 & \quad \max(|x|, |y|) < T \ \text{and}\ x\ne0, y\ne0 \\
    0 & \quad \max(|x|, |y|) > T \\
    \text{undefined} & \quad \text{otherwise}
  \end{array}
  \right.
\end{equation*}
A graphical diagram depicting this case is shown on \cref{fig:fss-square}. In
this case the algorithm described in \cref{sec:algo} gives a correct result in
any point which is few pixels away from where $F_{ss}$ is undefined.
\begin{figure}
  \centering
  \includegraphics[width=\linewidth]{images/fss-square.png}
  \caption[]{$F_{ss}$ function for a square with side $T$. The function is
    undefined along red segments. Its value is $2$ inside a shaded area and $0$
    outside.}
  \label{fig:fss-square}
\end{figure}

@@

\subsection{Gaussian mixture}
\label{sec:gauss}
\begin{figure}
  \centering
  \includegraphics[width=\linewidth, frame]{images/blob.png}
  \caption[]{An example of a ``blob'' generated by Gaussian mixture $f(x,y)$
    which consists of four Gaussian functions. White area is where
    $f(x,y) \le 3$.}
  \label{fig:blob}
\end{figure}
Take $N$ random values $a_i$, $b_i$ and $\sigma_i$. Let $f$ be
\begin{equation*}
  f(x,y) = \sum_{i=1}^N \frac{1}{\sigma_i} \exp(\frac{-(x-a_i)^2-(y-b_i)^2}{\sigma_i^2})
\end{equation*}
Inequality $f(x,y) \le T$ defines a ``blob'' like one which can be seen on
\cref{fig:blob}. We can use the algorithm developed in \cref{sec:cool-algo} to
compute precise values of $F_{ss}$ for this blob and compare them with values
obtained by using the fast algorithm in section \cref{sec:algo}. The result of
this comparison is on \cref{fig:fss-blob}. The maximal relative error for values
obtained with the fast algorithm is \textcolor{red}{insert value}.
\begin{figure*}[!pt]
  \centering
  \subfigure[$3\times 3$ kernel $H$]{
    \includegraphics[width=0.45\linewidth]{images/fss-blob-3x3.png}
    \label{fig:fss-blob-3x3}}
  \hfill
  \subfigure[$5\times 5$ kernel $H'$]{
    \includegraphics[width=0.45\linewidth]{images/fss-blob-5x5.png}
    \label{fig:fss-blob-5x5}}
  \caption[]{Plot of the surface-surface function for the blob on
    \cref{fig:blob}. Values of $F_{ss}$ were calculated in semi-circle with
    radius $R = 0.3$ and angle $\phi$ varying from $0$ to $\pi$. Resolution of
    the image varies from $500\times 500$ pixels to $3000\times 3000$.}
  \label{fig:fss-blob}
\end{figure*}

\section{Improvement of the fast algorithm}
\label{sec:improvement}
\begin{figure}
  \centering
  \includegraphics[width=\linewidth]{images/experiment-setup.png}
  \caption[]{Left, center: images $A$ and $B$ used in the experiment described
    in \cref{sec:improvement}. Right: Interfaces between phases are line
    segments which intersect each other at angle $\phi$. Shaded area is where
    $(H*A)\cdot(H*B)$ has non-zero values.}
  \label{fig:experiment-setup}
\end{figure}
Take two 2D images like the ones on \cref{fig:experiment-setup}. Boundaries
between black and white cross each other at the angle $\phi$. We apply the
filter $H$ (\cref{eq:filter-3x3-2d}) to each image, multiply results
element-wise and sum all elements of the product. An obtained value must
approximate $1/\sin \phi$ if we want $H$ to be suitable for calculation of
surface-surface function. With filter described in \cref{sec:algo} we get a
picture as on \cref{fig:angles-3x3}. We see that $H$ approximates
$1/\sin \phi$ not very good.

Now, let's try a wider filter $H'$:
\begin{align}
  H'_{ij} &= \frac{1}{30} \left[
    \begin{array}{ccccc}
      1 & 1 & 1 & 1 & 1 \\
      1 & 1 & 1 & 1 & 1 \\
      1 & 1 & -24 & 1 & 1 \\
      1 & 1 & 1 & 1 & 1 \\
      1 & 1 & 1 & 1 & 1 \\
    \end{array}
    \right] \label{eq:filter-5x5-2d} \\
  H'_{ijk} &= \frac{1}{150} \left[
    \begin{array}{ccccc}
      1 & 1 & 1 & 1 & 1 \\
      1 & 1 & 1 & 1 & 1 \\
      1 & 1 & 1 & 1 & 1 \\
      1 & 1 & 1 & 1 & 1 \\
      1 & 1 & 1 & 1 & 1 \\
    \end{array} ;
    \begin{array}{ccccc}
      1 & 1 & 1 & 1 & 1 \\
      1 & 1 & 1 & 1 & 1 \\
      1 & 1 & -124 & 1 & 1 \\
      1 & 1 & 1 & 1 & 1 \\
      1 & 1 & 1 & 1 & 1 \\
    \end{array} ;
    \begin{array}{ccccc}
      1 & 1 & 1 & 1 & 1 \\
      1 & 1 & 1 & 1 & 1 \\
      1 & 1 & 1 & 1 & 1 \\
      1 & 1 & 1 & 1 & 1 \\
      1 & 1 & 1 & 1 & 1 \\
    \end{array}
    \right] \label{eq:filter-5x5-3d}
\end{align}
With this filter we get a different picture (\cref{fig:angles-5x5}). A
comparison of the fast algorithm with a wider filter kernel with a precise
calculation for a ``blob'' show in \cref{sec:gauss} is show on
\cref{fig:fss-blob-5x5}. The maximal relative error is reduced to
\textcolor{red}{insert image}.
\begin{figure*}[!pt]
  \centering
  \subfigure[$3\times 3$ kernel $H$]{
    \includegraphics[width=0.45\linewidth]{images/angles-3x3.png}
    \label{fig:angles-3x3}}
  \hfill
  \subfigure[$5\times 5$ kernel $H'$]{
    \includegraphics[width=0.45\linewidth]{images/angles-5x5.png}
    \label{fig:angles-5x5}}
  \caption[]{dfdfdfdf}
  \label{fig:angles}
\end{figure*}

\section{Results}
\textcolor{red}{insert many pictures, also with different quality}

Unfortunately the filter $H'$ has some drawbacks in comparison with $H$. Firstly
$H$ has faster convergence with increase of image resolution. Our
acceptance criterion developed in \textcolor{red}{cite our paper again} works
also for $H'$, but sometimes it's possible to calculate a poor estimate of
$F_{ss}$ using $H$ but not $H'$. Secondly, $H'$ behaves worse that $H$ in points
of discontinuity of $F_{ss}$ as can be seen on \textcolor{red}{reference a
  picture where $F_{ss}$ is discontinuous}.

>>>>

\section{Problem of verification}
\label{sec:verify}
In paper \textcolor{red}{our paper} we tested these algorithms against known
analytic solutions. Although we obtained acceptable results in the cases of
overlapping balls and disks, we were not sure if our algorithm performs good in
general and searched for more test cases. Here we present one such case:
two-dimensional sets with smooth boundary.

\subsection{Surface-surface function in two-dimensional case}
\label{sec:fss-2d}
\begin{figure}
  \centering
  \includegraphics[width=0.8\linewidth]{images/Fss.png}
  \caption[]{Illustration of how $F_{ss}(\bm{r})$ is calculated. The interface
    between solid and void phases is a solid black curve. This interface
    translated by the vector $\bm{r}$ is show as a red solid curve. Support of
    $f_\Gamma(\bm{x}; \Delta)$ is a dashed ring. Shaded regions contribute to
    the surface-surface function.}
  \label{fig:Fss-explained}
\end{figure}
Let $S$ be some set in $\mathbb{R}^2$ which has a smooth boundary $\Gamma$ in
the sense that the boundary has a tangent line at every point. Now we introduce
a function $f_\Gamma(\bm{x}; \Delta)$:
\begin{equation*}
  f_\Gamma(\bm{x}; \Delta) = \left\{
  \begin{array}{ll}
    1/\epsilon & \quad \rho(\bm{x}, \Gamma) < \Delta \\
    0 & \quad \text{otherwise}
  \end{array}
  \right.
\end{equation*}
Here $\rho(\bm{x}, \Gamma)$ means a closest distance from point $\bm{x}$ to the
boundary $\Gamma$.

\begin{figure}
  \centering
  \includegraphics[width=0.8\linewidth]{images/fss-zoomed.png}
  \caption[]{Zoomed image of intersection between the interface $\Gamma$ and its
    translated version $\Gamma'$. $\phi$ is an angle between tangent lines to
    the interfaces. Surface of dashed area is $\frac{\Delta^2}{\sin \phi}$.}
  \label{fig:fss-zoomed}
\end{figure}
Now define a functional sequence $F_{ss}(\bm{x}; \Delta)$:
\begin{align*}
  F_{ss}(\bm{r}; \Delta) &= \int\int f_\Gamma(\bm{x}; \Delta) f_\Gamma(\bm{x}
  + \bm{r}; \Delta) dx dy \\
  &= \sum_{k=1}^N S_k/\Delta^2
\end{align*}
Here $N$ is a number of intersections of $\Gamma$ with itself translated by a
vector $\bm{r}$ and $S_k$ is a surface of each such intersection (see
\cref{fig:Fss-explained}).
When $\Delta$ tends to zero, the boundary at the point of intersection can
be replaced with a tangent line at the point of intersection
(\cref{fig:fss-zoomed}). We get an expression for a surface of
intersection: $S_k = \frac{\Delta^2}{\sin \phi_k}$ where $\phi_k$ is an
acute angle between tangent lines. Hence, we get the following equation:
\begin{equation}
  F_{ss}(\bm{r}) = \lim_{\Delta \to 0} F_{ss}(\bm{r}; \Delta) =
  \sum_{k=1}^N \frac{1}{\sin \phi_k} \label{eq:fss-2d}
\end{equation}
It's easy to show that
$\lim_{\Delta \to 0} f_\Gamma(\bm{x}; \Delta) = |\nabla \chi_S(\bm{x})|$
and therefore \cref{eq:fss-2d} and \cref{eq:fss} define the same function.

@@

\section{Examples of two-dimensional sets with smooth boundary}
\label{seq:examples}
In this section we will provide few examples of sets for which the developed
precise algorithm is applicable and compare the surface-surface function
calculated with the fast algorithm (\cref{sec:algo}) with results of the new
algorithm. We will use the filter $H$ (\ref{eq:filter-3x3-2d}) for edge
detection along with a new filter $H'$ (\ref{eq:filter-5x5-2d}) described in
\cref{sec:improvement}.

\subsection{A square}
Let's define a function $f(x, y) = \max(|x|, |y|)$. A set $f(x, y) \le T$ is a
square with side $2T$. The function $f$ is differentiable at all points where
$f(x, y) = T$ with exception of points $(-T, -T)$, $(-T, T)$, $(T, -T)$ and
$(T, T)$. The surface-surface correlation function for a square is equal to:
\begin{equation*}
  F_{ss}(x, y) = \left\{
  \begin{array}{ll}
    2 & \quad \max(|x|, |y|) < T \ \text{and}\ x\ne0, y\ne0 \\
    0 & \quad \max(|x|, |y|) > T \\
    \text{undefined} & \quad \text{otherwise}
  \end{array}
  \right.
\end{equation*}
A graphical diagram depicting this case is shown on \cref{fig:fss-square}. In
this case the algorithm described in \cref{sec:algo} gives a correct result in
any point which is few pixels away from where $F_{ss}$ is undefined.
\begin{figure}
  \centering
  \includegraphics[width=0.8\linewidth]{images/fss-square.png}
  \caption[]{$F_{ss}$ function for a square with side $T$. The function is
    undefined along red segments. Its value is $2$ inside a shaded area and $0$
    outside.}
  \label{fig:fss-square}
\end{figure}

@@

\subsection{Gaussian mixture}
\label{sec:gauss}
\begin{figure}
  \centering
  \includegraphics[width=0.8\linewidth, frame]{images/blob.png}
  \caption[]{An example of a ``blob'' generated by Gaussian mixture $f(x,y)$
    which consists of four Gaussian functions. White area is where
    $f(x,y) \le 3$.}
  \label{fig:blob}
\end{figure}
Take $N$ random values $a_i$, $b_i$ and $\sigma_i$. Let $f$ be
\begin{equation*}
  f(x,y) = \sum_{i=1}^N \frac{1}{\sigma_i} \exp(\frac{-(x-a_i)^2-(y-b_i)^2}{\sigma_i^2})
\end{equation*}
Inequality $f(x,y) \le T$ defines a ``blob'' like one which can be seen on
\cref{fig:blob}. We can use the algorithm developed in \cref{sec:cool-algo} to
compute precise values of $F_{ss}$ for this blob and compare them with values
obtained by using the fast algorithm in section \cref{sec:algo}. The result of
this comparison is on \cref{fig:fss-blob}.
\begin{figure*}[!pt]
  \centering
  \subfigure[$3\times 3$ kernel $H$]{
    \includegraphics[width=0.45\linewidth]{images/fss-blob-3x3.png}
    \label{fig:fss-blob-3x3}}
  \hfill
  \subfigure[$5\times 5$ kernel $H'$]{
    \includegraphics[width=0.45\linewidth]{images/fss-blob-5x5.png}
    \label{fig:fss-blob-5x5}}
  \caption[]{Plot of the surface-surface function for the blob on
    \cref{fig:blob}. Values of $F_{ss}$ were calculated in semi-circle with
    radius $R = 0.3$ and angle $\phi$ varying from $0$ to $\pi$. Resolution of
    the image varies from $500\times 500$ pixels to $3000\times 3000$.}
  \label{fig:fss-blob}
\end{figure*}

\subsection{Ellipses}
\label{sec:ellipses}
\begin{figure}
  \centering
  \includegraphics[width=0.8\linewidth, frame]{images/ellipses.png}
  \caption[]{An example of generated ellipses.}
  \label{fig:ellipses}
\end{figure}
Take $N$ random values $a_i$, $b_i$, $c_i$, $x^c_i$ and $y^c_i$ and define
\begin{equation*}
  f_i(x, y) = a_i(x-x^c_i)^2 + b(x-x^c_i)(y-y^c_i) + c_i(y-y^c_i)^2
\end{equation*}
with $a_ic_i - b_i^2 > 0$. Inequation
\begin{equation*}
  \min_i f_i(x, y) < A^2
\end{equation*}
defines $N$ ellipses like those which can be seen on \cref{fig:ellipses}. A
comparison between two algorithms is on \cref{fig:fss-ellipses}.
\begin{figure*}[!pt]
  \centering
  \subfigure[$3\times 3$ kernel $H$]{
    \includegraphics[width=0.45\linewidth]{images/fss-ellipses-3x3.png}
    \label{fig:fss-ellipses-3x3}}
  \hfill
  \subfigure[$5\times 5$ kernel $H'$]{
    \includegraphics[width=0.45\linewidth]{images/fss-ellipses-5x5.png}
    \label{fig:fss-ellipses-5x5}}
  \caption[]{Plot of the surface-surface function for ellipses on
    \cref{fig:ellipses}. Values of $F_{ss}$ were calculated in semi-circle with
    radius $R = 0.1$ and angle $\phi$ varying from $0$ to $\pi$. Resolution of
    the image varies from $500\times 500$ pixels to $3000\times 3000$.}
  \label{fig:fss-ellipses}
\end{figure*}

\section{Improvement of the fast algorithm}
\label{sec:improvement}
\begin{figure}
  \centering
  \includegraphics[width=0.8\linewidth]{images/experiment-setup.png}
  \caption[]{Left, center: images $A$ and $B$ used in the experiment described
    in \cref{sec:improvement}. Right: Interfaces between phases are line
    segments which intersect each other at angle $\phi$. Shaded area is where
    $(H*A)\cdot(H*B)$ has non-zero values.}
  \label{fig:experiment-setup}
\end{figure}
Take two 2D images like the ones on \cref{fig:experiment-setup}. Boundaries
between black and white cross each other at the angle $\phi$. We apply the
filter $H$ (\cref{eq:filter-3x3-2d}) to each image, multiply results
element-wise and sum all elements of the product. An obtained value must
approximate $1/\sin \phi$ if we want $H$ to be suitable for calculation of
surface-surface function. With filter described in \cref{sec:algo} we get a
picture as on \cref{fig:angles-3x3}. We see that $H$ approximates
$1/\sin \phi$ not very good.

Now, let's try a wider filter $H'$:
\begin{align}
  H'_{ij} &= \frac{1}{30} \left[
    \begin{array}{ccccc}
      1 & 1 & 1 & 1 & 1 \\
      1 & 1 & 1 & 1 & 1 \\
      1 & 1 & -24 & 1 & 1 \\
      1 & 1 & 1 & 1 & 1 \\
      1 & 1 & 1 & 1 & 1 \\
    \end{array}
    \right] \label{eq:filter-5x5-2d} \\
  H'_{ijk} &= \frac{1}{150} \left[
    \begin{array}{ccccc}
      1 & 1 & 1 & 1 & 1 \\
      1 & 1 & 1 & 1 & 1 \\
      1 & 1 & 1 & 1 & 1 \\
      1 & 1 & 1 & 1 & 1 \\
      1 & 1 & 1 & 1 & 1 \\
    \end{array} ;
    \begin{array}{ccccc}
      1 & 1 & 1 & 1 & 1 \\
      1 & 1 & 1 & 1 & 1 \\
      1 & 1 & -124 & 1 & 1 \\
      1 & 1 & 1 & 1 & 1 \\
      1 & 1 & 1 & 1 & 1 \\
    \end{array} ;
    \begin{array}{ccccc}
      1 & 1 & 1 & 1 & 1 \\
      1 & 1 & 1 & 1 & 1 \\
      1 & 1 & 1 & 1 & 1 \\
      1 & 1 & 1 & 1 & 1 \\
      1 & 1 & 1 & 1 & 1 \\
    \end{array}
    \right] \label{eq:filter-5x5-3d}
\end{align}
With this filter we get a different picture (\cref{fig:angles-5x5}). A
comparison of the fast algorithm with a wider filter kernel with a precise
calculation for a ``blob'' described in \cref{sec:gauss} is show on
\cref{fig:fss-blob-5x5}. A case with ellipses from \cref{sec:ellipses} is on
\cref{fig:fss-ellipses-5x5}.
\begin{figure*}[!pt]
  \centering
  \subfigure[$3\times 3$ kernel $H$]{
    \includegraphics[width=0.45\linewidth]{images/angles-3x3.png}
    \label{fig:angles-3x3}}
  \hfill
  \subfigure[$5\times 5$ kernel $H'$]{
    \includegraphics[width=0.45\linewidth]{images/angles-5x5.png}
    \label{fig:angles-5x5}}
  \caption[]{Estimation of $1/\sin\phi$ where $\phi$ is the angle between
    tangent lines to the interface by filters $H$ and $H'$.}
  \label{fig:angles}
\end{figure*}

\section{Results}
With the new filter calculation of $F_{ss}$ becomes more precise, even for
three-dimensional images. This can be seen in comparison with theoretical values
for known cases like the one of overlapping balls \textcolor{red}{insert plot}.

Unfortunately the filter $H'$ has some drawbacks in comparison with $H$. Firstly
$H$ has faster convergence with increase of image resolution. Our
acceptance criterion developed in \textcolor{red}{cite our paper again} works
also for $H'$, but sometimes it's possible to calculate a poor estimate of
$F_{ss}$ using $H$ but not $H'$. Secondly, $H'$ behaves worse that $H$ in points
of discontinuity of $F_{ss}$ as can be seen on \cref{fig:fss-disk}.
